%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Java Backend Developer} % Job title
    {Negah Tech. Holding of Karafarin Bank} % Organization
    {Tehran, Iran} % Location
    {Sep. 2020 - Present} % Date(s)
    {
      \begin{cvprojects}
        \cvproject{Legacy Internet Bank Project}{ % Project name
          \begin{projectitems} % Description(s) of tasks/responsibilities
            \item {Maintenance and development of the legacy Internet Bank project of Karafarin Bank.}
            \item {Written in Groovy language wih Grails framework for Backend.}
            \item {Written in HTML/CSS/JavaScript language with Jquery framework for Frontend.}
            \item {Using MVC architecture and Oracle 10g as database.}
          \end{projectitems}
        }
        \cvproject{New Unified Omni-Channel Platform Project}{ % Project name
          \begin{projectitems} % Description(s) of tasks/responsibilities
            \item {Backend development of the Omni-Channel project of Karafarin Bank to create a unified backend platform for web and mobile clients to connect.}
            \item {Written in Java language with Spring Boot framework, using Oracle relational DB, MongoDB NoSql DB and Redis cache.}
            \item {Using JPA on top of Hibernate for running simple ORM tasks.}
            \item {Using Retrofit and RestTemplate as http client, MapStruct and ModelMapper for mapping between Entities and DTOs, and QueryDSL for executing complex queries.}
            \item {Utilizing 4-layers backend architecture (controller, facade, service, repository).}
            \item {Consultation on hiring developers for the mobile team.}
          \end{projectitems}
        }
      \end{cvprojects}
    }

%---------------------------------------------------------
  \cventry
    {Senior Android Developer} % Job title
    {Carpino, \nth{3} Ride Hailing app in Iran} % Organization
    {Tehran, Iran} % Location
    {Jun. 2019 - Apr. 2020} % Date(s)
    {
    	  \begin{cvprojects}
    	    \cvproject{Rewrite of Carpino-Passenger android app from scratch}{ % Project name
    	      \begin{projectitems} % Description(s) of tasks/responsibilities
    	        \item {Using Kotlin language with Room ORM and and SQLite DB.}
    	        \item {Utilizing 3-layers MVVM android architecture with LiveData observables.}
    	        \item {Using modern libraries like Dagger-Android dependency injection and Retrofit http client.}
    	      \end{projectitems}
    	    }
    	    \cvproject{Carpino-Driver android app}{ % Project name
    	      \begin{projectitems} % Description(s) of tasks/responsibilities
    	        \item {Development of intelligent map systems for driver app, like a 3D navigation system similar to Waze but with GPS nosie cancellation and Hotzones showing high ride demands.}
    	        \item {Collecting usage and crash data using Firebase Analytics, old Google Analytics, Crashlytics and Adtrace.}
    	        \item {Using 3-layers MVC android architecture with RxJava async library, Retrofit http client and various third party UI libraries.
}
    	      \end{projectitems}
    	    }
    	  \end{cvprojects}
    }

%---------------------------------------------------------
  \cventry
    {IT Support (Compulsory Military Service)} % Job title
    {Iran's Army Aviation Forces, MND} % Organization
    {Tehran, Iran} % Location
    {Feb. 2018 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintenance and management of software, OS, hardware and network of 400+ desktop clients.}
        \item {Managing Active Directory and Windows File Sharing servers.}
        \item {Administration and configuration of Cisco switches and routers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Game Developer Intern at Global Internship Program} % Job title
    {NEXON} % Organization
    {Seoul, S.Korea \& LA, U.S.A} % Location
    {Jan. 2013 - Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed in Cocos2d-x an action puzzle game(Dragon Buster) targeting U.S. market.}
        \item {Implemented API server which is communicating with game client and In-App Store, along with two other team members who wrote the game logic and designed game graphics.}
        \item {Won the 2nd prize in final evaluation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {ShitOne Corp.} % Organization
    {Seoul, S.Korea} % Location
    {Dec. 2011 - Feb. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a proxy drive smartphone application which connects proxy driver and customer.}
        \item {Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Penetration Tester} % Job title
    {SAMSUNG Electronics} % Organization
    {S.Korea} % Location
    {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
        \item {Conducted penetration testing on SAMSUNG Smart TV.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
